Refinement of Thermostated Molecular Dynamics via Backward Error Analysis

### 2018-06-16 rigid_bodies.tex
add Bussi results
Small changes in the figure with thermodynamics properties

It seems then reasonable to argue that a NHC thermostat should regulate the shadow kinetic energy instead of the specified one.
However, the theory underlying the concept of shadow Hamiltonian is only applicable to symplectic integrators, whereas NHC thermostats introduce non-Hamiltonian components to the equations of motion.
In this paper, we devise a novel procedure that partially overcomes this limitation.
It consists in using a splitting-based numerical integrator that entails a Hamiltonian component and carrying out backward error analysis out of this NVE part only.
This allows us to obtain, with minimal computational overhead, a \textit{refined kinetic energy} and a \textit{refined Hamiltonian} as suitable estimators of their shadow counterparts.
By recasting the thermostat equations with this refined kinetic energy, we are able to predict its equipartition and to reproduce a canonical ensemble consistent with the refined Hamiltonian.
Finally, a reweighting procedure provides us with ensemble averages which are, instead, consistent with the specified one. It should be emphasized that this approach is not limited to deterministic thermostats. It would be straightforward to use it, for instance, in conjunction with global stochastic thermostats such as those of Bussi \textit{et al}. \cite{Bussi_2007} and Leimkuhler \textit{et al}. \cite{Leimkuhler_2009}, for instance.

@@

In the previous section, we have seen that drifts in the extended energy of an NVT simulation can accumulate in the thermostat-related variables, thus preventing full-fledged instability from happening.
This allows simulations to be executed with large time steps, which could in principle save computer time.
However, as we will show now, discretization errors can become manifest much earlier than any risk of instability.
Fortunately, our proposed methodology is capable of mitigating the effect of these errors on the ensemble averages computed for the simulated system.

>>>>

It seems then reasonable to argue that a NHC thermostat should regulate the shadow kinetic energy instead of the specified one.
However, the theory underlying the concept of shadow Hamiltonian is only applicable to symplectic integrators, whereas NHC thermostats introduce non-Hamiltonian components to the equations of motion.
In this paper, we devise a novel procedure that partially overcomes this limitation.
It consists in using a splitting-based numerical integrator that entails a Hamiltonian component and carrying out backward error analysis out of this NVE part only.
This allows us to obtain, with minimal computational overhead, a \textit{refined kinetic energy} and a \textit{refined Hamiltonian} as suitable estimators of their shadow counterparts.
By recasting the thermostat equations with this refined kinetic energy, we are able to predict its equipartition and to reproduce a canonical ensemble consistent with the refined Hamiltonian.
Finally, a reweighting procedure provides us with ensemble averages which are, instead, consistent with the specified one. It should be emphasized that this approach is not limited to deterministic thermostats. It is straightforward to use it, for instance, in conjunction with global stochastic thermostats such as those of Bussi \textit{et al}. \cite{Bussi_2007} and Leimkuhler \textit{et al}. \cite{Leimkuhler_2009}, for instance.

@@

In the previous section, we have seen that drifts in the extended energy of an NVT simulation can accumulate in the thermostat-related variables, thus preventing full-fledged instability from happening.
This allows simulations to be executed with large time steps, which could in principle be used to save computer time.
However, as we will show in this section, discretization errors can become manifest much earlier than does any risk of instability.
Fortunately, our proposed methodology is capable of mitigating the effect of these errors on the ensemble averages computed for the simulated system.
